Lay Perceptions of Crowd-Scientific Findings: The Risks of Variability and Lack of Consensus

### 2021-10-07 talk/index.Rmd
further edits studies table

`r icon_style(icons::fontawesome("users"), scale = 2, fill = "#035AA6")` $~~$ Also known as the **many-analysts** or **multi-analyst** approach
`r icon_style(icons::fontawesome("chart-line"), scale = 2, fill = "#035AA6")` $~~~~$ On the **rise** in behavioral science

@@

```{r, echo = FALSE}
t1 <- data.frame(
  Authors = c(
    "Botvinik-Nezer et al.",
    "Schweinsberg et al.",
    "Silberzahn et al."
  ),
  Year = c(
    2020,
    2018,
    2018
  ),
  Title = c(
    "Variability in the analysis of a single neuroimaging dataset by many teams",
    "Same data, different conclusions: Radical dispersion in empirical results when independent analysts operationalize and test the same hypothesis",
    "Many Analysts, One Data Set: Making Transparent How Variations in Analytic Choices Affect Results"
  )
)
DT::datatable(t1, fillContainer = FALSE, options = list(pageLength = 2))
```

---
# Open Science Statement

>>>>

`r icon_style(icons::fontawesome("users"), scale = 2, fill = "#035AA6")` $~~$ Also known as the **many-analysts** or **multi-analyst** approach
`r icon_style(icons::fontawesome("chart-line"), scale = 2, fill = "#035AA6")` $~~~~$ On the **rise** in the social and behavioral sciences

@@

```{r, echo = FALSE}
t1 <- data.frame(
  Authors = c(
    "Bastiaansen et al.",
    "Botvinik-Nezer et al.",
    "Breznau et al.",
    "Breznau et al.",
    "Huntington-Klein et al.",
    "Schweinsberg et al.",
    "Silberzahn et al."
  ),
  Year = c(
    2019,
    2020,
    2021,
    2021,
    2020,
    2018,
    2018
  ),
  Title = c(
    "Time to get personal? The impact of researchers choices on the selection of
treatment targets using the experience sampling methodology",

    "Variability in the analysis of a single neuroimaging dataset by many teams",

    "How many replicators does it take to achieve reliability? Investigating researcher variability in a crowdsourced replication",

    "Observing many researchers using the same data and hypothesis
reveals a hidden universe of uncertainty",

    "The influence of hidden researcher decisions in applied microeconomics",

    "Same data, different conclusions: Radical dispersion in empirical results when independent analysts operationalize and test the same hypothesis",

    "Many analysts, one data set: Making transparent how variations in analytic choices affect results"
  ) 
) %>% 
  arrange(desc(Year))

DT::datatable(t1, fillContainer = FALSE, options = list(pageLength = 2))
```

# Open Science Statement
